Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
_

\subsection{Infrastructure Software}
Software developed to better utilize new infrastructure and architectures,
e.g., \emph{MVAPICH}, \emph{visIT}. Explores uncharted territories. Highest
risk since the projects are experimental. Successful projects reap high rewards
and have longer usage span. By nature, they overlap with the utility software
as they must serve as a facilitator to run ordinary codes. Long
requirement-development-test cycles.  Wide community support but tends to be
handled by specialists rather then end users. Promotes collaborations across
the breadth (eg. different departments) and depth (eg. stakeholders within a
department) of community, one of the key ingredient of a sustainable process.
Ferenbaugh~\cite{Ferenbaugh_WSSSPE} discusses the risks and challenges
associated with software projects dealing with new architectures. To leverage
the power of accelerators such as GPUs and MICs new code and libraries are
required. The experience of efforts as described in~\cite{Ferenbaugh_WSSSPE}
met with a limited success but nonetheless with many invaluable lessons were
learned about cultural and technical aspects in sustainable software
development practices.

>>>>

\subsection{Infrastructure Software}
%TODO: expand
Software developed to better utilize new infrastructure and architectures,
e.g., \emph{MVAPICH}, \emph{visIT}. Explores uncharted territories. Highest
risk since the projects are experimental. Successful projects reap high rewards
and have longer usage span. By nature, they overlap with the utility software
as they must serve as a facilitator to run ordinary codes. Long
requirement-development-test cycles.  Wide community support but tends to be
handled by specialists rather then end users. Promotes collaborations across
the breadth (eg. different departments) and depth (eg. stakeholders within a
department) of community, one of the key ingredient of a sustainable process.
Ferenbaugh~\cite{Ferenbaugh_WSSSPE} discusses the risks and challenges
associated with software projects dealing with new architectures. To leverage
the power of accelerators such as GPUs and MICs new code and libraries are
required. The experience of efforts as described in~\cite{Ferenbaugh_WSSSPE}
met with a limited success but nonetheless with many invaluable lessons were
learned about influential cultural and technical aspects in sustainable software
development practices.

Summary of above discussed cases: lessons, trends, commonalities, is there an
ideal sustainability scenario?
